MSDS 7333 Case Study 06

### 2017-06-19 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Added table of contents and mention of dragons
I am tired.

### Table of Contents:
<li>[Assignment Requirements](#AssignmentOutline)</li>
<li>[Introduction](#Introduction)</li>
<li>[Part 1](#Part1)</li>
  <li>[Signal Collection](#SigCol)</li>
  <li>[Signal Strength](#SigStren)</li>
  <li>[Signal Density](#SigDen)</li>
  <li>[Discussion](#Discussion)</li>
<li>[Part2](#Part 2)</li>

@@

### Part 1
#### The Approach (Explained)

@@

To fully answer this question, we will need to explore exactly what is happening with each MAC address. The results of this exploration will define the parameters needed for such a decision.

#### Here we will create a Signal Collection Map
For this exercise, we will plot both the count and locations of the signals recorded for the access points. Even though it would be ideal to plot the access points(APs) directly on the map, we do not know their X and Y coordinates.

@@

#### Signal Strength Distributions
Plotting the individual signal strength distributions for each AP angle will help add perspective to the information we are working with. For the sake of consistency, we will use the same stationary coordinates listed in the course book (coord : (2, 12)) <font color = "red">(Add reference here.)</font>

@@

#### Time to investigate Signal Density
To properly investigate the difference between these two addresses, the signal strength densities for each address should be plotted for each 45 degree angle. This will help display the defining characteristics for each address. The location used for this analysis is the (24,4) from the book.

@@

@@

#### We now have enough information to address these questions before an analysis of kNN is conducted:

The evidence would suggest both addresses should be kept within the analysis to increase the coverage for the entire spectrum of strengths. The address chosen to be rejected not only has a lower signal strength when measured from either end of the building, it also shows to have a higher signal density when it is further away from the receiver. The address chosen to be kept has a higher signal density closer to the receivers. By keeping both addresses, the model should be able to generate a more accurate prediction of the layout of the building. This theory will be tested as we tour through k-Nearest Neighbors.

#### Let's dive into the K-Nearest Neighbors:
<font color = "red"><b>Discuss KNN here</b></font>

@@

```{r}
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```
This output shows the signal strengths at each angle. This will be useful later!
<font color = "red"><b>&uarr;Explain why &uarr;</b></font>

@@

> for k-NN, we will include training data with angles close to point in question since angle matters.
> if we want one angle, then include angles that match the rounded orientation of new observation.
> if we want two angles, then pick two multiples of 45 degrees that flank the new observation's orientation.
> if we want three angles, then pick the closest 45 degree increment and on either side of it.
> what if we didn't want to collapse the signal strengths across the m angles, and
> instead return a set of mx166 signals for each access point?

@@

@@

@@

#Part 2: Alternatvie k-Nearest Neighbors
</a>
```{r}
# create weights for neighbors based on signal strength and multiple times X and Y and sum neighbors
# to get X and Y.
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[ , 4],
               offlineSummary, numAngles = 3, k = 5, weighted=TRUE)
actXY = onlineSummary[ , c("posX", "posY")]
calcError(estXY, actXY)
```

>>>>

### Table of Contents:
<li>[Assignment Requirements](#AssignmentOutline)</li>
<li>[Introduction](#Introduction)</li>
<li>[**Part 1**](#Part1)</li> 
<ul> 
  <li>[Signal Collection](#SigCol)</li>
  <li>[Signal Strength](#SigStren)</li>
  <li>[Signal Density](#SigDen)</li>
  <li>[Discussion](#Discussion)</li>
  <li>[k-Nearest Neighbors](#knn)</li>
</ul>
<li>[**Part 2**](#Part 2)</li>

@@

***
<a id='Part1'>

### Part 1</a>  
#### The Approach (Explained)

@@

To fully answer this question, we will need to explore exactly what is happening with each MAC address. The results of this exploration will define the parameters needed for such a decision.
<a id='SigCol'>

#### Here we will create a Signal Collection Map</a>
For this exercise, we will plot both the count and locations of the signals recorded for the access points. Even though it would be ideal to plot the access points(APs) directly on the map, we do not know their X and Y coordinates.

@@

***
<a id='SigStren'>

#### Signal Strength Distributions</a>
Plotting the individual signal strength distributions for each AP angle will help add perspective to the information we are working with. For the sake of consistency, we will use the same stationary coordinates listed in the course book (coord : (2, 12)) <font color = "red">(Add reference here.)</font>

@@

***
<a id='SigDen'>

#### Time to investigate Signal Density</a>
To properly investigate the difference between these two addresses, the signal strength densities for each address should be plotted for each 45 degree angle. This will help display the defining characteristics for each address. The location used for this analysis is the (24,4) from the book.

@@

***
<a id='Discussion'>

### Discussion</a>
#### We now have enough information to address these questions before an analysis of kNN is conducted:

The evidence thus far would suggest both addresses should be kept within the analysis to increase the coverage for the entire spectrum of strengths. The address chosen to be rejected not only has a lower signal strength when measured from either end of the building, but it also shows to have a higher signal density when it is further away from the receiver. The address chosen to be kept has a higher signal density closer to the receivers with the accompanying higher signal strengths. By keeping both addresses, the model should be able to generate a more accurate prediction of the layout of the building. This theory will be tested as we tour k-Nearest Neighbors.

@@

<a id='knn'>

#### Let's dive into the K-Nearest Neighbors:</a>

<font color = "red"><b>Discuss KNN here</b></font>

@@

With the unique MAC addresses in hand, an accurate profile of the different signal strengths reveived by angle is able to be determined. This can be done with the following code: 
```{r}
online = readData("online.final.trace.txt", subMacs = macs)
online$posXY = paste(online$posX, online$posY, sep = "-")
length(unique(online$posXY))
tabonlineXYA = table(online$posXY, online$angle)
#output shows measurements were taken at all angles throughout the floor
tabonlineXYA
```
This output shows the signal strengths at each angle. This will be useful later!
<font color = "red"><b>&larr;Explain why &larr;</b></font>

@@

<font color = "purple">
(this can probably be removed)

> for k-NN, we will include training data with angles close to point in question since angle matters.
> if we want one angle, then include angles that match the rounded orientation of new observation.
> if we want two angles, then pick two multiples of 45 degrees that flank the new observation's orientation.
> if we want three angles, then pick the closest 45 degree increment and on either side of it.
> what if we didn't want to collapse the signal strengths across the m angles, and
> instead return a set of mx166 signals for each access point?
</font>

@@

<font color="red"><b>&uarr;We will need to discuss these results&uarr;</b></font>

@@

### **Here be Dragons &darr;**

@@

#Part 2: Alternative k-Nearest Neighbors
</a>
```{r}
# create weights for neighbors based on signal strength and multiple times X and Y and sum neighbors
# to get X and Y.
estXY = predXY(newSignals = onlineSummary[ , 6:12],
               newAngles = onlineSummary[ , 4],
               offlineSummary, numAngles = 3, k = 5, weighted=TRUE)
actXY = onlineSummary[ , c("posX", "posY")]
calcError(estXY, actXY)
```
